%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Minimalist Professional Resume Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,10pt]{article}

%-----------------------------
% Packages and Settings
%-----------------------------
\usepackage[margin=1in]{geometry}      % Set page margins
\usepackage{enumitem}                  % Custom list environments
\usepackage{hyperref}                  % For hyperlinks
\usepackage{xcolor}                    % For colored text/links
\usepackage{parskip}                   % Better paragraph spacing
\usepackage[T1]{fontenc}
\usepackage{lmodern}                   % Improved font rendering

\usepackage{parskip}
\setlength{\parskip}{0.25em}

% Uncomment the next line for a modern sans-serif look:
% \renewcommand{\familydefault}{\sfdefault}

% Section title formatting: uppercase and a rule underneath
\usepackage{titlesec}
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]

%-----------------------------
% Custom Commands
%-----------------------------
% Command for header entries with a title and date on the same line
\newcommand{\resumeEntry}[2]{%
  \noindent\textbf{#1} \hfill \textit{#2}\par\vspace{-0.5ex}%
}

%-----------------------------
% Document Content
%-----------------------------
\begin{document}
\pagestyle{empty}
\small

%-----------------------------
% Header: Name and Contact Information
%-----------------------------
\begin{center}
    {\LARGE \textbf{Tyler Jensen}}\\[2mm]
    \small
    \href{mailto:tyjensen222@gmail.com}{tyjensen222@gmail.com} \textbullet\ 
    (303) 888-4604 \textbullet\ Ca\~{n}on City, CO \\
    \href{https://www.linkedin.com/in/tyler-jensen-923130181}{LinkedIn} \textbullet\ 
    \href{https://github.com/yourprofile}{GitHub}
\end{center}

\vspace{0.25cm}

%-----------------------------
% Experience Section
%-----------------------------
\section*{Experience}

\resumeEntry{Senior Data Analyst, Engrain}{Oct 2024 -- Present}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Built and maintained a collection of PowerBI dashboards giving stakeholders key insights into a variety of
    KPIs across the organization, enabling managment and C-Suite members to make data-driven decisions.
    \item Built and maintained a variety of automations using Python and Workato employing a myraid of APIs to streamline product onboarding, implementation,
    and delivery.
    \item Used OpenAI's APIs to fine-tune vision and customer support tasks, and deployed them to key systems.
    \item Developed and deployed an auto-tasking application using Python that solved a Linear Programming problem to optimally
    partition tasks in a work queue to corresponding team members and automate assignment via API.
    Used Streamlit to deploy the app for use by management across multiple departments.
\end{itemize}

\resumeEntry{Data Analyst, Engrain}{May 2023 -- Oct 2024}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Spearheaded a data cleanse initiative across all key systems in the organization to prepare for 
    a state-of-the-art customer portal.
    \item Built and maintained a Vector Database using Pinecone and OpenAI to assist in fuzzy searching, duplicate detection, and record linkage tasks.
    \item Built and maintained multiple internal Python libraries to enable peers to easily interface
    with a variety of critical APIs.
    \item Won multiple employee recognition awards.
\end{itemize}

\resumeEntry{Data Integrations Specialist, Engrain}{August 2022 -- May 2023}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Built Python tools to interface with our clients' property managment software and internal APIs.
    \item Configured and maintained live pricing and availability API feeds.
\end{itemize}

\resumeEntry{Intern, Presidio}{June 2019 -- August 2019}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Documented and distributed a knowledge base on IoT/OT devices to contribute to a sales strategy 
    targeting correlated markets.
\end{itemize}

%-----------------------------
% Education Section
%-----------------------------
\section*{Education}

\resumeEntry{Colorado State University - B.S., Mathematics}{2022}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Coursework Highlights:} Post-Quantum Cryptography, Algebraic Topology, Lie Groups
    \item Worked as a Teaching Assistant for Mathematical Cryptography and Abstract Algebra courses.
\end{itemize}

%-----------------------------
% Skills Section
%-----------------------------
\section*{Skills}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Coding:} Python, Pandas, git, Docker, SQL, PyTorch, scikit-learn, M, DAX, LaTeX
    \item \textbf{Software/APIs:} Workato, PowerBI, Salesforce, Workfront, NetSuite, OpenAI, Pinecone, Google
\end{itemize}

%-----------------------------
% Projects Section
%-----------------------------
\section*{Projects}

\resumeEntry{Personal Study}{Present}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Ongoing study to complete all exercises in Nathan Carter's \textit{Data Sciense for Mathematicians},
    Allen Hatcher's \textit{Algebraic Topology}, and Kristopher Tapp's \textit{Matrix Groups for Undergraduates}.
\end{itemize}

\resumeEntry{Minitorch}{2024}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Followed the instructive repository \href{https://minitorch.github.io/}{minitorch}, which builds the 
    fundamental infrastructure of the PyTorch API from scratch.
\end{itemize}

\resumeEntry{Undergraduate Mathematics Research}{2021-2022}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Under the guidance of Henry Adams, contributed to a research project on embeddings of low-dimensional manifolds 
    via the Laplace-Beltrami operator (e.g. Laplacian Eigenmaps).
\end{itemize}

\end{document}